SAT Competition 2020\tnoteref{title}

### 2021-02-01 paper/main.tex
aspell

This article focuses on the 2020 instantiation of the SAT competitions. 
To this end, we provide
a detailed account of SAT Competition 2020 in terms of organizational details, competition tracks,
participating solvers, benchmarks, and the empirical results from the competition.
In terms of competition tracks, two new tracks, namely the cloud track and an application-specifc track, where introduced in 2020 
in addition to the already earlier established main, parallel, and incremental tracks; we
provide motivation and the new organizational details for both of the tracks.
In terms of solvers, we provide an overview of solving strategies and other details implemented in top-performing solvers
from the competition, complementing the individual solver descriptions available in the 2020 competition proceedings.
 As for benchmarks, we describe how the 2020 benchmark sets were constructed for each of the competition tracks, with 
an overview of the benchmarks contributed to the 2020 competition.
In terms of empirical results we provide further analysis on the results going beyond the standard rankings provided
on the SAT competition webpages (\url{https://satcompetition.github.io/2020/}). 
Finally, we also provide a discussion on lessons learned and ideas for future editions of SAT competitions.

@@

Finally, the Main Track also had the so-called ``Glucose hack'' sub-track. 
Since in the past several advances in SAT solving required only a small modification of an established solver
to achieve a considerable contribution, this sub-track encouraged participation 
of small modifications of the Glucose 3.0 SAT solver. The limit for being considered a ``hack''
was set to 1000 non-space character edit distance from the sources of Glucose provided by the organisers. 
Unfortunately, in 2020 there were not enough participants in this sub-track and we do not report on it 
in the results section.

@@

In the Incremental Library track we mimic scenarios
where a SAT solver is used as a backend solver in a more complex tool
(typically solving a harder problem than SAT) and is called multiple times before 
the enclosing tool reaches its final state. Incrementality means that
the individual calls to the SAT solver are not independent, but may share 
a common subset of the input clauses or differ in the presence of additional 
unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.

@@

The Parallel track evaluates solver performance in wallclock time on multiple cores.
The benchmarks and the timeout (5000 seconds) are the same as in the Main track. 
Each solver run in this track was on a m4.16xlarge machine from Amazon Web Services (AWS).
These machines have 64 virtual cores and 256GB of memory. In contrast to the 
Main track, there is no proof logging for unsatisfiable benchmarks in the Parallel track.

@@

New this year was the Cloud track to evaluated distributed solvers. Similar to the
Parallel track, the solvers ran on the Amazon cloud, but using 100 machines of the
type m4.4xlarge, which have 16 virtual cores and 64GB of memory. 
Communication between the machines is possible using MPI and SSH.
The wallclock timeout is 1000 seconds and the same benchmarks were used as in
the Main and Parallel track.

@@

As noted above, the Parallel track was run on AWS m4.16xlarge machines with 64 virtual CPUs and 256 GB
of memory, while the Cloud track was run on AWS m4.4xlarge machines with 16 virtual CPUs and 64 GB of
memory. These tracks used wallclock timeouts of \SI{5000}{\second} and \SI{1000}{\second}, respectively.

@@

Finding the minimal makespan $i$ for which $F_i$ is satisfiable is important for
SAT-based planning in general and the generation of this benchmark set in
particular. The minimal makespan depends on the planning task and the used
encoding. The hardest formulas that a SAT-based planner has to solve are usually
the last unsatisfiable $F_i$ before the next higher makespan $i$ is satisfiable
\cite{Rintanen2006}. Therefore we preferably pick the last unsatisfiable
makespan for each planning task to generate unsatisfiable instances. For
planning tasks where this makespan cannot be determined with available
computational resources, we use a \emph{sequential} encoding, where the minimal
makespan equals the length of the shortest valid plan. Together with known
bounds\footnote{Bounds on plan length are available for some planning tasks from
  the \emph{optimal track} that have \emph{unit cost} actions.} on the optimal
plan length we can generate SAT formulas with predetermined satisfiability for
hard planning problems.

@@

The classical planning benchmarks are selected from the \emph{satisficing} and
\emph{optimal} tracks of the \emph{International Planning Competitions} 2014
\footnote{\url{https://helios.hud.ac.uk/scommv/IPC-14/repository/benchmarksV1.1.zip}}
and 2018 \footnote{\url{https://bitbucket.org/ipc2018-classical/domains}}.

@@

% - 86 out of 100 biggest (number of clauses) are planning
% - 109 / 200 in the planning track are not solved by any solver
% - 186 / 600 in total
% - all 200 above 90\% binary clauses and half have above 99%
The instances of the Planning track are big compared to the main track
instances. Using the number of clauses as a metric; out of the $100$ biggest
instances of both tracks
% of the main-track
$86$ belong to the Planning track. The large size can mainly be attributed to
binary clauses. On average, more than $98$\% of the clauses are binary for
planning instances. The average for the Main track instances is below $60$\%.

@@

Table \ref{tab:planningBenchmarkDist} shows the number of benchmarks generated
by each encoding. 
For a complete list of the encoded planning tasks we refer to the
generation script.\footnote{\url{https://satcompetition.github.io/2020/downloads/planning_generator.tar.xz}} 
The benchmarks of the planning track adhere to the following naming convention:
${\langle \texttt{SAT/UNSAT} \rangle\_\langle \texttt{encoding} \rangle\_\langle
  \texttt{name} \rangle\_\langle \texttt{makespan}
  \rangle\text{.cnf}}$

@@

The incremental library track was introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017. 
Benchmarks for the Incremental Library track constist of \emph{benchmark applications} which implement and use the incremental SAT solver in their backend as well as \emph{benchmark instances} which serve as input to these applications. 
For evaluating the Incremental Library track, we used six applications which implement the IPASIR interface -- ranging from determination of backbone variables to SAT-based planning. 
For each of those applications, we individually selected $50$ problem instances serving as input for the respective application.

@@

Four solver participating in the Main track (\solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alliup-trial}, and \solver{CMS-ccnr-lsids}) 
performed significantly better compared to the others, see Table~\ref{tab:results}.
Figure~\ref{main:all} shows the cumulative solved instances plot of the best performing solver of the strongest
10 teams (in short, the top 10 solvers)  together with the Virtual Best Solver (VBS).
The four top solvers all have a different code base, which is rare and has not been observed in many years.
Also, in recent competitions, the top solvers were much closer together.
The winning solver is \solver{Kissat-sat} and the runner-up is \solver{Relaxed-newTech}. Notice that 
\solver{Relaxed-newTech} solved more instances within the 2000 seconds limit.
The third place, based on the PAR-2 score, was for \solver{CMS-ccnr-lsids}. It solved two fewer instances
compared to \solver{CaDiCaL-alliup-trial}, but solved various formulas much more efficiently. 
Since the SAT Competition started to rank based on the PAR-2 score, such cases have been observed several times.

@@

The winning solver in the Parallel track is \solver{Painless-MCOMSPS-STR32}. The number in the postfix denotes
that this solver used 32 threads on the 64 virtual cores that were available. It has been observed in earlier 
competitions that uses fewer threads than the number of virtual cores can be helpful as threads compete 
for memory, which can reduce of the overall performance. The runner up is \solver{Plingeling}, while the
third place is for \solver{ManyGlucose-32}. Figure~\ref{fig:res-parallel} shows the performance of
all participating parallel solvers. Notice in Table~\ref{tab:results} that only the \solver{Painless-MCOMSPS-STR} solvers
and \solver{Plingeling} had a lower PAR-2 score than the winner of the Main Track (\solver{Kissat-sat}). 
This shows that it is hard to beat sequential solvers with a parallel solver on the competition instances. 
We will show later in the article (Table~\ref{tab:tuples}) that small sequential portfolios 
perform better (in terms of PAR-2 score) than the parallel solvers.

@@

The clear winner of the Cloud track is \solver{Mallob-Mono} and the runner-up is \solver{TopoSAT2},
see Figure~\ref{fig:res-cloud}.
\solver{Mallob-Mono} was able to solver more instances in 1000 seconds, compared to the 
winner of the Parallel Track in 5000 seconds, thereby showing the potential of distributed SAT solving. 
The other four participants performed significantly worse. This is likley due to the initial challenges
to develop a distributed solver. This was the first year of this track. We expect that the gap will be 
closer is future years.

@@

In SAT Competition 2017, Luo et al. integrated learnt clause minimization based on unit propagation (\solver{LCM}) in their award winning \solver{Maple\_LCM\_Dist}~\cite{Luo:2017:LCM} which also uses the new branching heuristic \solver{Distance (Dist)} in an initial solving period~\cite{Xiao:2017:MapleLCMDist}. 
Using \solver{Maple\_LCM\_Dist}, Ryvchin and Nadel successfully integrated conditional chronological backtracking (\solver{ChronoBT})~\cite{Nadel:2018:CBT}. 
They presented their award winning \solver{Maple\_LCM\_Dist\_ChronoBT} in SAT Competition~2018~\cite{Ryvchin:SC2018:MapleChronoBT}.

@@

Many independent and award-winning code-bases can be found among the SAT solvers written by Biere. 
The sequential SAT solver \solver{Lingeling} has been award winning since SAT Competition~2011 and is still competitive in its parallel version \solver{Plingeling}~\cite{Biere:2012:Lingeling}. 
As of SAT Competition~2017, \solver{CaDiCaL} % \cite{Biere:SC2020} - or cite some older proceedings to match the "As of SAT Competition~2017" part?
by Biere is another independent, award winning and structured implementation of the state-of-the-art in SAT solving. 
Its improved reimplementation \solver{Kissat}~\cite{Biere:SC2020} won in several of this competitions sequential tracks by a large margin.

@@

\solver{Kissat} is a low-level reimplementation of \solver{CaDiCaL} with new sophisticated lazy data-structures for clause state monitoring, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2019,Biere:SC2020}. 
Moreover, forward subsumption for learned clauses is mostly replaced by vivification algorithms~\cite{ChuMinLi:2020:Vivification}.

@@

The \solver{F2TRC} fork of \solver{MapleLCMDistCBT} achieved the third best score on unsatisfiable instances. 
\solver{F2TRC} comes with deterministic reimplementations of former winning strategies in \solver{Maple}, e.g., by replacing time-based intervals through conflict-based intervals~\cite{Kochemazov:SC2020}.

@@

\solver{ManyGlucose} was submitted in \solver{32} and \solver{64} threaded variants. 
The \solver{32} threaded variant received two awards in this competition: the overall third place and third best score on unsatisfiable instances. 
\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behaviour~\cite{Audemard:2018:GlucoseSyrup}~\cite{Audemard:2014:LazyClauseExchange}~\cite{Hamadi:2009:ManySat}.

@@

\solver{Painless Maple} received the award for the second best performance on satisfiable instances but had the worst performance on unsatisfiable instances. 
\solver{Painless Maple} integrates the solver \solver{ExMapleLCMDistChronoBT} into the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless}. 
\solver{Painless Maple} uses a sharing strategy in which the solvers are divided into those which only export clauses and others which import \emph{and} export clauses. 
\solver{Painless Maple} was submitted in two variants \solver{v1} and \solver{v2}. 
\solver{Painless Maple v1} diversifies via hand-crafted heuristic configurations and \solver{Painless Maple v2} diversifies via randomized intialization of branching heuristics~\cite{SC2020}.

@@

\solver{Mallob} is a fork of the generic massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSATs}. 
\solver{Mallob} performs dynamic load balancing through \emph{malleable job scheduling} in case the input contains several SAT instances of varying priorty. 
This functionality is disabled in the submitted variant \solver{Mallob Mono}. 
\solver{Mallob} uses \solver{Lingeling-bcj} and as every 14th solver \solver{Mallob} spawns the SLS solver \solver{YalSAT}~\cite{Biere:2018:LingelingYalsat}.
Diversification is done via randomized sparse initialization of branching scores.

@@

Contributions to the VBS can be well capatured by clustering the instance space into instance families. 
We evaluated the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf. Table~\ref{tab:families}) and report on their place and score in Table~\ref{tab:eval-by-family}. 
Interestingly, the overall winning solver \solver{Kissat-sat} is outperformed by the second and third ranked solvers \solver{Relaxed-newTech} and \solver{CMS-ccnr-lsids} on the \emph{Anti-Bandwidth}, \emph{Vlsat}, and \emph{Influence Maximization} families by a large margin.

@@

% \begin{equation}
% \label{eq-similarity}
\[
	similarity(S, S') =\quad 1 - \frac{\sum{|S_{i} - S'_{i}|}}{316 \cdot \num{10000}}
\]
% \end{equation}
We calculated the \emph{similarity} of the $30$ solvers with the
best average PAR-2 score in the main track. The results are displayed in
Figure~\ref{fig-similarity-main} as a \emph{heat map}, similar to the visualization in \cite{Balyo:2015:SATRace}. Additionally, the result
of hierarchically clustering the solvers based on their similarity is
illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
are joined reflects how similar they are. For example, enabling the \emph{trail
  saving} in \solver{CaDiCaL-alluip} has no impact on the runtime, resulting in
a similarity above \num{0.999}. Therefore the two solvers are joined low in the
dendrogram.
% A similar visualization was used for the results of the SAT Race 2015 \cite{Balyo:2015:SATRace}.

One big cluster that we identify consists of the \solver{Maple}-decedents,
all of which are modifications of the winners in the SAT Competition 2018 and
the SAT Race 2019.
The similarity within the cluster is high, with the exception of
\solver{Scavel} and \solver{exp\_V\_MLD\_CBT\_DL}.
They form a subcluster
with a lower similarity to the rest, but a high similarity within. In fact, the highest measured similarity,
 % of $0.96$
besides the aforementioned \solver{CaDiCaL-alluip}, is observed between them.
The two solvers are both based on
\solver{MapleLCMDistChronoBT-dl-v2.2} but have different authors.
The high similarity suggest that the
changes they made either result in a very similar behavior or do not have a
significant impact on the runtime performance.

The two configurations of \solver{Relaxed} by \emph{Zhang} and \emph{Cai}
use the same codebase as a lot of solvers in the Maple-Cluster but their
overall performance is better and closer to the \solver{CMS}-Cluster.
The three \solver{CMS} configurations
differ in their implementation of stochastic local search
(SLS) and have similar performance.
The 2020 version of \solver{CaDiCaL}
performed worse than the modifications based on the 2019 version and
does not quite fit into any cluster.

@@

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{similarity/cross.pdf}
    \caption{Heat-map and dendrogram (top) based on the runtime similarity of the solvers participating in the main track.
      Darker regions mean that the solvers are more similar.
      A more precise relation between color and similarity-value together with a histogram of the values that appear is given at the bottom.
    }
    \label{fig-similarity-main}
\end{figure}

% \subsection{Solver Ranking Robustness}
\subsection{Influence of Benchmark Selection on Solver Ranking}
The main result of the competition is the ranking of the solvers participating
in the main track, according to their average PAR-2 score. To evaluate the impact
of benchmark selection on the solver ranking, we follow the experiments
described in the tool suite
\texttt{benchfeature}\cite{benchfeature}.
% \footnote{\url{http://fmv.jku.at/benchfeature/}} developed
% by Fazekas, Kaufmann and Biere.
% performed the following
% experiment:

@@

All winning solvers of the \emph{Main} track periodically schedule runs of an SLS solver and import statistical information generated in unsuccessul SLS runs to reconfigure weights in their branching heuristics.

As can be seen in the \emph{Parallel} track, it is hard to scale SAT solving beyond $32$ threads, as in some occassions the $32$ threaded version of the same solver outperformed its $64$ threaded counterpart. 
However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture.

@@

Many prominent applications of SAT use an \emph{incremental} SAT solver in their backend. 
Those incremental use-cases impose additional challenges on solver authors. 
The emergence of new fuzzing tools for incremental SAT solvers based on IPASIR can help researchers with also integrating and testing their methods in the incremental use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}

@@

\section*{Acknowledgements}
The authors thank StarExec for their support and resources to run the Main and the Planning tracks, and Amazon Web Services 
for their support and resources to run the Parallel and Cloud tracks.

>>>>

This article focuses on the 2020 instantiation of the SAT competitions. 
To this end, we provide
a detailed account of SAT Competition 2020 in terms of organizational details, competition tracks,
participating solvers, benchmarks, and the empirical results from the competition.
In terms of competition tracks, two new tracks, namely the cloud track and an application-specific track, where introduced in 2020 
in addition to the already earlier established main, parallel, and incremental tracks; we
provide motivation and the new organizational details for both of the tracks.
In terms of solvers, we provide an overview of solving strategies and other details implemented in top-performing solvers
from the competition, complementing the individual solver descriptions available in the 2020 competition proceedings.
 As for benchmarks, we describe how the 2020 benchmark sets were constructed for each of the competition tracks, with 
an overview of the benchmarks contributed to the 2020 competition.
In terms of empirical results we provide further analysis on the results going beyond the standard rankings provided
on the SAT competition web pages (\url{https://satcompetition.github.io/2020/}). 
Finally, we also provide a discussion on lessons learned and ideas for future editions of SAT competitions.

@@

Finally, the Main Track also had the so-called ``Glucose hack'' sub-track. 
Since in the past several advances in SAT solving required only a small modification of an established solver
to achieve a considerable contribution, this sub-track encouraged participation 
of small modifications of the Glucose 3.0 SAT solver. The limit for being considered a ``hack''
was set to 1000 non-space character edit distance from the sources of Glucose provided by the organizers. 
Unfortunately, in 2020 there were not enough participants in this sub-track and we do not report on it 
in the results section.

@@

In the Incremental Library track we mimic scenarios
where a SAT solver is used as a back-end solver in a more complex tool
(typically solving a harder problem than SAT) and is called multiple times before 
the enclosing tool reaches its final state. Incremental means that
the individual calls to the SAT solver are not independent, but may share 
a common subset of the input clauses or differ in the presence of additional 
unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.

@@

The Parallel track evaluates solver performance in wall-clock time on multiple cores.
The benchmarks and the timeout (5000 seconds) are the same as in the Main track. 
Each solver run in this track was on a m4.16xlarge machine from Amazon Web Services (AWS).
These machines have 64 virtual cores and 256GB of memory. In contrast to the 
Main track, there is no proof logging for unsatisfiable benchmarks in the Parallel track.

@@

New this year was the Cloud track to evaluated distributed solvers. Similar to the
Parallel track, the solvers ran on the Amazon cloud, but using 100 machines of the
type m4.4xlarge, which have 16 virtual cores and 64GB of memory. 
Communication between the machines is possible using MPI and SSH.
The wall-clock timeout is 1000 seconds and the same benchmarks were used as in
the Main and Parallel track.

@@

As noted above, the Parallel track was run on AWS m4.16xlarge machines with 64 virtual CPUs and 256 GB
of memory, while the Cloud track was run on AWS m4.4xlarge machines with 16 virtual CPUs and 64 GB of
memory. These tracks used wall-clock timeouts of \SI{5000}{\second} and \SI{1000}{\second}, respectively.

@@

Finding the minimal makespan $i$ for which $F_i$ is satisfiable is important for
SAT-based planning in general and the generation of this benchmark set in
particular. The minimal makespan depends on the planning task and the used
encoding. The hardest formulas that a SAT-based planner has to solve are usually
the last unsatisfiable $F_i$ before the next higher makespan $i$ is satisfiable
\cite{Rintanen2006}. Therefore we preferably pick the last unsatisfiable
makespan for each planning task to generate unsatisfiable instances. For
planning tasks where this makespan cannot be determined with available
computational resources, we use a \emph{sequential} encoding, where the minimal
makespan equals the length of the shortest valid plan. Together with known
bounds\footnote{Bounds on plan length are available for some planning tasks from
  the \emph{Optimal track} that have \emph{unit cost} actions.} on the optimal
plan length we can generate SAT formulas with predetermined satisfiability for
hard planning problems.

@@

The classical planning benchmarks are selected from the \emph{satisfying} and
\emph{Optimal} tracks of the \emph{International Planning Competitions} 2014
\footnote{\url{https://helios.hud.ac.uk/scommv/IPC-14/repository/benchmarksV1.1.zip}}
and 2018 \footnote{\url{https://bitbucket.org/ipc2018-classical/domains}}.

@@

% - 86 out of 100 biggest (number of clauses) are planning
% - 109 / 200 in the planning track are not solved by any solver
% - 186 / 600 in total
% - all 200 above 90\% binary clauses and half have above 99%
The instances of the Planning track are big compared to the Main track
instances. Using the number of clauses as a metric; out of the $100$ biggest
instances of both tracks
% of the main-track
$86$ belong to the Planning track. The large size can mainly be attributed to
binary clauses. On average, more than $98$\% of the clauses are binary for
planning instances. The average for the Main track instances is below $60$\%.

@@

Table \ref{tab:planningBenchmarkDist} shows the number of benchmarks generated
by each encoding. 
For a complete list of the encoded planning tasks we refer to the
generation script.\footnote{\url{https://satcompetition.github.io/2020/downloads/planning_generator.tar.xz}} 
The benchmarks of the Planning track adhere to the following naming convention:
${\langle \texttt{SAT/UNSAT} \rangle\_\langle \texttt{encoding} \rangle\_\langle
  \texttt{name} \rangle\_\langle \texttt{makespan}
  \rangle\text{.cnf}}$

@@

The Incremental Library track was introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017.
Benchmarks for the Incremental Library track consist of \emph{benchmark applications} which implement and use the incremental SAT solver in their back-end as well as \emph{benchmark instances} which serve as input to these applications. 
For evaluating the Incremental Library track, we used six applications which implement the IPASIR interface -- ranging from determination of backbone variables to SAT-based planning. 
For each of those applications, we individually selected $50$ problem instances serving as input for the respective application.

@@

Four solver participating in the Main track (\solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trial}, and \solver{CMS-ccnr-lsids}) 
performed significantly better compared to the others, see Table~\ref{tab:results}.
Figure~\ref{main:all} shows the cumulative solved instances plot of the best performing solver of the strongest
10 teams (in short, the top 10 solvers)  together with the Virtual Best Solver (VBS).
The four top solvers all have a different code base, which is rare and has not been observed in many years.
Also, in recent competitions, the top solvers were much closer together.
The winning solver is \solver{Kissat-sat} and the runner-up is \solver{Relaxed-newTech}. Notice that 
\solver{Relaxed-newTech} solved more instances within the 2000 seconds limit.
The third place, based on the PAR-2 score, was for \solver{CMS-ccnr-lsids}. It solved two fewer instances
compared to \solver{CaDiCaL-alluip-trial}, but solved various formulas much more efficiently. 
Since the SAT Competition started to rank based on the PAR-2 score, such cases have been observed several times.

@@

The winning solver in the Parallel track is \solver{Painless-MCOMSPS-STR32}. The number in the post-fix denotes
that this solver used 32 threads on the 64 virtual cores that were available. It has been observed in earlier 
competitions that uses fewer threads than the number of virtual cores can be helpful as threads compete 
for memory, which can reduce of the overall performance. The runner up is \solver{Plingeling}, while the
third place is for \solver{ManyGlucose-32}. Figure~\ref{fig:res-parallel} shows the performance of
all participating parallel solvers. Notice in Table~\ref{tab:results} that only the \solver{Painless-MCOMSPS-STR} solvers
and \solver{Plingeling} had a lower PAR-2 score than the winner of the Main Track (\solver{Kissat-sat}). 
This shows that it is hard to beat sequential solvers with a parallel solver on the competition instances. 
We will show later in the article (Table~\ref{tab:tuples}) that small sequential portfolios 
perform better (in terms of PAR-2 score) than the parallel solvers.

@@

The clear winner of the Cloud track is \solver{Mallob-Mono} and the runner-up is \solver{TopoSAT2},
see Figure~\ref{fig:res-cloud}.
\solver{Mallob-Mono} was able to solver more instances in 1000 seconds, compared to the 
winner of the Parallel Track in 5000 seconds, thereby showing the potential of distributed SAT solving. 
The other four participants performed significantly worse. This is likely due to the initial challenges
to develop a distributed solver. This was the first year of this track. We expect that the gap will be 
closer is future years.

@@

In SAT Competition 2017, Luo et al. integrated learned clause minimization based on unit propagation (\solver{LCM}) in their award winning \solver{Maple\_LCM\_Dist}~\cite{Luo:2017:LCM} which also uses the new branching heuristic \solver{Distance (Dist)} in an initial solving period~\cite{Xiao:2017:MapleLCMDist}. 
Using \solver{Maple\_LCM\_Dist}, Ryvchin and Nadel successfully integrated conditional chronological backtracking (\solver{ChronoBT})~\cite{Nadel:2018:CBT}. 
They presented their award winning \solver{Maple\_LCM\_Dist\_ChronoBT} in SAT Competition~2018~\cite{Ryvchin:SC2018:MapleChronoBT}.

@@

Many independent and award-winning code-bases can be found among the SAT solvers written by Biere. 
The sequential SAT solver \solver{Lingeling} has been award winning since SAT Competition~2011 and is still competitive in its parallel version \solver{Plingeling}~\cite{Biere:2012:Lingeling}. 
As of SAT Competition~2017, \solver{CaDiCaL} % \cite{Biere:SC2020} - or cite some older proceedings to match the "As of SAT Competition~2017" part?
by Biere is another independent, award winning and structured implementation of the state-of-the-art in SAT solving. 
Its improved re-implementation \solver{Kissat}~\cite{Biere:SC2020} won in several of this competitions sequential tracks by a large margin.

@@

\solver{Kissat} is a low-level re-implementation of \solver{CaDiCaL} with new sophisticated lazy data-structures for clause state monitoring, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2019,Biere:SC2020}. 
Moreover, forward subsumption for learned clauses is mostly replaced by vivification algorithms~\cite{ChuMinLi:2020:Vivification}.

@@

The \solver{F2TRC} fork of \solver{MapleLCMDistCBT} achieved the third best score on unsatisfiable instances. 
\solver{F2TRC} comes with deterministic re-implementations of former winning strategies in \solver{Maple}, e.g., by replacing time-based intervals through conflict-based intervals~\cite{Kochemazov:SC2020}.

@@

\solver{ManyGlucose} was submitted in \solver{32} and \solver{64} threaded variants. 
The \solver{32} threaded variant received two awards in this competition: the overall third place and third best score on unsatisfiable instances. 
\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behavior~\cite{Audemard:2018:GlucoseSyrup}~\cite{Audemard:2014:LazyClauseExchange}~\cite{Hamadi:2009:ManySat}.

@@

\solver{Painless Maple} received the award for the second best performance on satisfiable instances but had the worst performance on unsatisfiable instances. 
\solver{Painless Maple} integrates the solver \solver{ExMapleLCMDistChronoBT} into the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless}. 
\solver{Painless Maple} uses a sharing strategy in which the solvers are divided into those which only export clauses and others which import \emph{and} export clauses. 
\solver{Painless Maple} was submitted in two variants \solver{v1} and \solver{v2}. 
\solver{Painless Maple v1} diversifies via hand-crafted heuristic configurations and \solver{Painless Maple v2} diversifies via randomized initialization of branching heuristics~\cite{SC2020}.

@@

\solver{Mallob} is a fork of the generic massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSATs}. 
\solver{Mallob} performs dynamic load balancing through \emph{malleable job scheduling} in case the input contains several SAT instances of varying priority. 
This functionality is disabled in the submitted variant \solver{Mallob Mono}. 
\solver{Mallob} uses \solver{Lingeling-bcj} and as every 14th solver \solver{Mallob} spawns the SLS solver \solver{YalSAT}~\cite{Biere:2018:LingelingYalsat}.
Diversification is done via randomized sparse initialization of branching scores.

@@

Contributions to the VBS can be well captured by clustering the instance space into instance families. 
We evaluated the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf. Table~\ref{tab:families}) and report on their place and score in Table~\ref{tab:eval-by-family}. 
Interestingly, the overall winning solver \solver{Kissat-sat} is outperformed by the second and third ranked solvers \solver{Relaxed-newTech} and \solver{CMS-ccnr-lsids} on the \emph{Anti-Bandwidth}, \emph{Vlsat}, and \emph{Influence Maximization} families by a large margin.

@@

% \begin{equation}
% \label{eq-similarity}
\[
	similarity(S, S') =\quad 1 - \frac{\sum{|S_{i} - S'_{i}|}}{316 \cdot \num{10000}}
\]
% \end{equation}
We calculated the \emph{similarity} of the $30$ solvers with the
best average PAR-2 score in the Main track. The results are displayed in
Figure~\ref{fig-similarity-main} as a \emph{heat map}, similar to the visualization in \cite{Balyo:2015:SATRace}. Additionally, the result
of hierarchically clustering the solvers based on their similarity is
illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
are joined reflects how similar they are. For example, enabling the \emph{trail
  saving} in \solver{CaDiCaL-alluip} has no impact on the runtime, resulting in
a similarity above \num{0.999}. Therefore the two solvers are joined low in the
dendrogram.
% A similar visualization was used for the results of the SAT Race 2015 \cite{Balyo:2015:SATRace}.

One big cluster that we identify consists of the \solver{Maple}-decedents,
all of which are modifications of the winners in the SAT Competition 2018 and
the SAT Race 2019.
The similarity within the cluster is high, with the exception of
\solver{Scavel} and \solver{exp\_V\_MLD\_CBT\_DL}.
They form a sub-cluster
with a lower similarity to the rest, but a high similarity within. In fact, the highest measured similarity,
 % of $0.96$
besides the aforementioned \solver{CaDiCaL-alluip}, is observed between them.
The two solvers are both based on
\solver{MapleLCMDistChronoBT-dl-v2.2} but have different authors.
The high similarity suggest that the
changes they made either result in a very similar behavior or do not have a
significant impact on the runtime performance.

The two configurations of \solver{Relaxed} by \emph{Zhang} and \emph{Cai}
use the same code-base as a lot of solvers in the Maple-Cluster but their
overall performance is better and closer to the \solver{CMS}-Cluster.
The three \solver{CMS} configurations
differ in their implementation of stochastic local search
(SLS) and have similar performance.
The 2020 version of \solver{CaDiCaL}
performed worse than the modifications based on the 2019 version and
does not quite fit into any cluster.

@@

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{similarity/cross.pdf}
    \caption{Heat-map and dendrogram (top) based on the runtime similarity of the solvers participating in the Main track.
      Darker regions mean that the solvers are more similar.
      A more precise relation between color and similarity-value together with a histogram of the values that appear is given at the bottom.
    }
    \label{fig-similarity-main}
\end{figure}

% \subsection{Solver Ranking Robustness}
\subsection{Influence of Benchmark Selection on Solver Ranking}
The main result of the competition is the ranking of the solvers participating
in the Main track, according to their average PAR-2 score. To evaluate the impact
of benchmark selection on the solver ranking, we follow the experiments
described in the tool suite
\texttt{benchfeature}\cite{benchfeature}.
% \footnote{\url{http://fmv.jku.at/benchfeature/}} developed
% by Fazekas, Kaufmann and Biere.
% performed the following
% experiment:

@@

All winning solvers of the \emph{Main} track periodically schedule runs of an SLS solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics.

As can be seen in the \emph{Parallel} track, it is hard to scale SAT solving beyond $32$ threads, as in some occasions the $32$ threaded version of the same solver outperformed its $64$ threaded counterpart. 
However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture.

@@

Many prominent applications of SAT use an \emph{incremental} SAT solver in their back-end. 
Those incremental use-cases impose additional challenges on solver authors. 
The emergence of new fuzzing tools for incremental SAT solvers based on IPASIR can help researchers with also integrating and testing their methods in the incremental use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}

@@

\section*{Acknowledgments}
The authors thank StarExec for their support and resources to run the Main and the Planning tracks, and Amazon Web Services 
for their support and resources to run the Parallel and Cloud tracks.
